Molecular Analysis

### 2023-10-03 analysis/mol_analysis.Rmd
revise transmission chain plot

@@

tnet_pl <- tnet %>%
  ggplot(aes(y = date_infection, x = virus, fill = virus, size = n)) +
  facet_wrap(~ class, ncol = 2, scales = "free_x") +
  geom_point(shape = 21, color = "black") +
  geom_segment(aes(y = from, yend = to, xend = virus), size = 1,
               arrow = arrow(length = unit(0.2, "cm")), color = "black") +
  labs(size = "No. of infections", fill = "Virus", title = "c") +
  coord_y_datetime(ylim = c(max(tnet$date_infection), min(tnet$date_infection))) +
  scale_y_datetime(date_breaks = "1 week", date_labels = "%b %d") +
  scale_size_discrete(range = c(4,8)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.spacing = unit(1, "cm"),
        panel.grid.major.x = element_line(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 10, margin = margin(b = 10))) #+
  #guides(fill = "none")

#save_plot(tnet_pl, "../results/mol-data/network-plot.pdf", w = 16, h = 20)
```

```{r}
# combine
descr <- pos_tot_pl + plot_spacer() + pos_cond_pl & theme(legend.position = "bottom", legend.key.height = unit(.1, "cm"),
                                          legend.key.width = unit(.3, "cm"))
descr <- descr + plot_layout(guides = "collect", widths = c(9.5, 1, 5.5), ncol = 2) 
descr <- descr + tnet_pl 
descr <- descr + plot_layout(nrow = 2, heights = c(4, 16), design = 'ABC
                             DDD')
save_plot(descr, pdf_file = "../results/mol-data/descriptives.pdf", eps_file = "../results/mol-data/descriptives.eps", h = 22, w = 16)
# saveRDS(pos_tot_pl + ggtitle(""), file = "../results/mol-data/descriptives-total.rds")
# saveRDS(pos_cond_pl + ggtitle(""), file = "../results/mol-data/descriptives-cond.rds")
# saveRDS(pos_week_pl + ggtitle(""), file = "../results/mol-data/descriptives-week.rds")
```

>>>>

```{r}
# combine
descr <- pos_tot_pl + plot_spacer() + pos_cond_pl & theme(legend.position = "bottom", legend.key.height = unit(.1, "cm"),
                                          legend.key.width = unit(.3, "cm"))
descr <- descr + plot_layout(guides = "collect", widths = c(9.5, 1, 5.5), ncol = 2) 
descr <- descr + pos_week_pl 
descr <- descr + plot_layout(nrow = 2, heights = c(8, 8), design = 'ABC
                             DDD')
save_plot(descr, pdf_file = "../results/mol-data/descriptives.pdf", eps_file = "../results/mol-data/descriptives.eps", h = 16, w = 16)
# saveRDS(pos_tot_pl + ggtitle(""), file = "../results/mol-data/descriptives-total.rds")
# saveRDS(pos_cond_pl + ggtitle(""), file = "../results/mol-data/descriptives-cond.rds")
# saveRDS(pos_week_pl + ggtitle(""), file = "../results/mol-data/descriptives-week.rds")
```

@@

tnet_pl <- tnet %>%
  ggplot(aes(y = date_infection, x = virus, fill = virus, size = n)) +
  facet_wrap(~ class, ncol = 2, scales = "free_x") +
  geom_point(shape = 21, color = "black") +
  geom_segment(aes(y = from, yend = to, xend = virus), size = 1,
               arrow = arrow(length = unit(0.2, "cm")), color = "black") +
  labs(size = "No. of infections", fill = "Virus", title = "c") +
  coord_y_datetime(ylim = c(max(tnet$date_infection), min(tnet$date_infection))) +
  scale_y_datetime(date_breaks = "1 week", date_labels = "%b %d") +
  scale_size_discrete(range = c(4,8)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.box = "vertical",
        plot.title.position = "plot",
        axis.title = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        panel.spacing = unit(1, "cm"),
        panel.grid.major.x = element_line(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 10, margin = margin(b = 10))) +
  guides(fill = "none",
         size = guide_legend(nrow = 1, order = 1))

save_plot(tnet_pl, pdf_file = "../results/mol-data/network-plot.pdf", eps_file = "../results/mol-data/network-plot.eps", w = 16, h = 22)
```
